---
title: "Economy or Security, US or China"
author: 
   - George Yin
   - Iain Johnston
   - Chia-hung Tsai
   
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    fig_caption: yes
    latex_engine: xelatex
    includes:
      in_header: header.tex
  html_notebook:
    highlight: textmate
    number_sections: yes
    theme: spacelab
    toc: yes
  html_document:
    df_print: paged
    toc: yes
editor_options:
  chunk_output_type: inline
bibliography: ['bibimmigration.bib','bibpolarization.bib']
biblio-stype: 'apsr'
link-citations: true
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, collapse = TRUE,
                       latex.options.color='blue')
knitr::write_bib(c("knitr","stringr"), "", width=60)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE}
library(tidyverse)
library(stargazer)
library(foreign); library(ggplot2); library(tidyverse); library(readstata13)
library(ggcorrplot)
library(mediation)
library(MASS)
options(stringsAsFactors = F)
```


# Introduction


# Cross-Strait Relations

# Literature Review

# Data and Hypotheses
We draw national land-line numbers randomly and conduct a telephone survey between November 14 and 18, 2019. There are 1,222 completions. 



# Descriptive Analysis
## Distribution
```{r echo=FALSE}
load('PP1997B1.Rdata')
```


```{r fig.showtext = TRUE, fig.align='center',fig.cap="\\label{fig:figs}Relationship w/ China or U. S. for National Security"}
barplot(100*table(choice1)/1222)
```

```{r fig.showtext = TRUE, fig.align='center',fig.cap="\\label{fig:figs}Relationship w/ China or U. S. for Economy"}
barplot(100*table(choice2)/1222)
```

## Cross-tabulation 

```{r fig.showtext = TRUE, fig.align='center',fig.cap="\\label{fig:figs}Economy and Security"}
DT <-data.frame(Economy=choice1, Security=choice2)
require(gridExtra)
DT <-na.omit(DT) 
plot1<-ggplot(aes(x = Economy, fill = Security), data=DT) +
  geom_bar(position = "fill") +
  scale_y_continuous(name = "Within group Percentage"
                     , labels = scales::percent) 
plot2<-ggplot(aes(fill = Economy, x = Security), data=DT) +
  geom_bar(position = "fill") +
  scale_y_continuous(name = "Within group Percentage"
                     , labels = scales::percent) 
grid.arrange(plot1, plot2, nrow=2)
```


# Data Analysis
```{r  results='asis'}
load('PP1997B1.Rdata')
newdata<-data.frame(choice1, choice2, influence, USintervene,  male.n, age1, age2, education, panblue, pangreen)
newdata<-na.omit(newdata)
opm1<-polr(choice1 ~ influence +  USintervene 
       + panblue + pangreen
       + male.n + age1 + age2 + education, 
        data=newdata)

opm2<-polr(choice2 ~ influence +  USintervene 
       + panblue + pangreen
       + male.n + age1 + age2 + education, 
        data=newdata)

stargazer(opm1, opm2, title="Better Relationship w/ China for National Security and Economy",  
          dep.var.labels=c("National Security", "Economy"),
         covariate.labels=c('Influence of China',
        "US intervention", "Pan-blue", "Pan-green", 
        "Male", "20-39 yrs", "40-59 yrs","Education"), header=F, no.space = TRUE, style = 'io')
```



```{r  results='asis'}
load('PP1997B1.Rdata')
newdata<-data.frame(choice1, choice2, influence, USintervene, panblue, pangreen, male.n, age1, age2, education)
newdata<-na.omit(newdata)
om1<-polr(choice1 ~ influence +  USintervene 
       + influence:USintervene + panblue + pangreen
       + male.n + age1 + age2 + education, 
        data=newdata)

om2<-polr(choice2 ~ influence +  USintervene 
       + influence:USintervene + panblue + pangreen
       + male.n + age1 + age2 + education, 
        data=newdata)

stargazer(om1, om2, title="Better Relationship w/ China for National Security and Economy",  
          dep.var.labels=c("National Security", "Economy"),
         covariate.labels=c('Influence of China',
        "US intervention", "Interaction", "Pan-blue", "Pan-green",
        "Male", "20-39 yrs", "40-59 yrs","Education"), header=F, no.space = TRUE, style = 'io')
```

## Two Ordered Probit Models
```{r  results='asis'}
load('PP1997B1.Rdata')
newdata<-data.frame(choice1, choice2, influence, USintervene, feeling, uni, kmt, dpp, Tsai, male.n, age1, age2,
          education)
newdata<-na.omit(newdata)
m1<-polr(choice1 ~ influence + feeling + USintervene 
       + influence:USintervene +feeling  +  uni + kmt + dpp  + Tsai
       + male.n + age1 + age2 + education, 
        data=newdata)

m2<-polr(choice2 ~ influence +  USintervene 
       + influence:USintervene +  feeling + uni + kmt + dpp + Tsai
       + male.n + age1 + age2 + education, 
        data=newdata)

stargazer(m1, m2, title="Better Relationship w/ China for National Security and Economy",  
          dep.var.labels=c("National Security", "Economy"),
         covariate.labels=c('Influence of China',
        "US intervention", "Interaction", "Feeling about China", 
        "Unification",
        "KMT identification", "DPP identification", "Tsai's performance",
        "Male", "20-39 yrs", "40-59 yrs","Education"), header=F, no.space = TRUE, style = 'io')
```
# Conclusion

# Appendix
## Question wording

 - Influence
 
 Do you think the U.S. or China has more influence in Asia?

 - Economy
 
 Regarding Taiwan's economy, do you think Taiwan should have better relationship with the U.S. or China?

 - National security
 
 Regarding Taiwan's national security, do you think Taiwan should  have better relationship with the U.S. or China?

 - Feeling about China
 
 From 0 to 10, where 0 means that you strongly dislike and 10 means that you strongly like, what is your feeling about China?
 
  - Taiwanese/Chinese identity
  
  Do you think of yourself as Taiwanese, Chinese, or both?
  
  - Partisanship
  
  In our society, there are many political parties. Which party do you identify with?
  
  - Economy or sovereignty (es)
  
  If we cannot handle economy and sovereignty at the same time, which one do you think is more important for our country?
  
  - US intervene
  
  If Taiwan declares independence and China attacks Taiwan, do you think the U.S. would remains
neutral, hesitate, or send troops to help Taiwan?
  
  - Tsai's performance
  
  In general, are you satisfied or dissatisfied with President Tsai's performance for past three years?
  
  - trade
  
  Regarding the cross-Strait trade, do you think our government should be more open or strengthen the regulation?
  



# References


